\PYGEOMETRY{}: a Python library for the creation of Monte Carlo radiation transport physical geometries

### 2020-09-16 public/paper/pyg4ometry.tex
delete comma
replacing pyinline with verb looks better in this instance

\section{Rapid geometry modelling}
Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
the parameters of the geometry and visualise it.  When a user has achieved the desired geometry, without geometry overlaps, a GDML file can be written to file 
from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
users of Geant4 or GDML, apart from the new class described in the previous section called the \pyinline{Registry}. First the \verb|Registry| is created to store all 
the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved
as a GDML file or visualised using VTK.

>>>>

\section{Rapid geometry modelling}
Given the Python scripting interface, expression  and tessellation engines it is possible for a user to rapidly specify the geometrical layout of the RT problem, vary 
the parameters of the geometry and visualise it.  When a user has achieved the desired geometry without geometry overlaps, a GDML file can be written to file 
from the internal memory representation. Some example code is presented in Listing~\ref{lst:pythonRapidModelling}. The structure should be familiar to regular 
users of Geant4 or GDML, apart from the new class described in the previous section called the \verb|Registry|. First the \verb|Registry| is created to store all 
the \PYGEOMETRY{} objects; followed by constants;  then materials and properties, solids and logical and physical volumes; finally the whole geometry can be saved
as a GDML file or visualised using VTK.
